The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
Project

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

## Schematic of workflow

@@

Table 1. Baseline Characteristics of IPTp Trial Participants

```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

# Render the table in DOCX-compatible format
kable(
  table_data,
  format = "pandoc",
  caption =
)

@@

Figure 1: Distribution of Total Malaria Episodes

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(ggplot2)

# Create a histogram of total malaria episodes
ggplot(data = promo_data_clean, aes(x = total_malaria_episodes)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Total Malaria Episodes",
    x = "Total Malaria Episodes",
    y = "Count"
  )
```

@@

## Exploratory/Descriptive analysis

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below. I generally recommend the `here` package.

>>>>

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
bibliography: "../../assets/dataanalysis-references.bib"
csl: "../../assets/american-journal-of-epidemiology.csl"

format:
  docx:
    toc: true
    number-sections: true
    output-file: "Manuscript.docx"

project:
  output-dir: "C:/Users/ajose35/Desktop/MADA-course/Joseph-MADA-project/products/manuscript"

execute:
  echo: false
  warning: false
  message: false
---

@@

@@

**Table 1. Baseline Characteristics of IPTp Trial Participants**
```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

kable(
  table_data,
  format = "pandoc",
  caption =
) %>%
  kable_styling(full_width = FALSE, position = "center")

@@

&nbsp;
&nbsp;

**Figure 1: Distribution of Total Malaria Episodes**
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(ggplot2)

# Create a histogram of total malaria episodes
ggplot(data = promo_data_clean, aes(x = total_malaria_episodes)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(
    title =,
    x = "Total Malaria Episodes",
    y = "Count"
  )
```

@@
